---
title: "Hands-On Exercise 4"
description: |
  Hands-On exercise to practice ggstatsplot and visualize uncertainty
author:
  - name: Tan Jit Kai
    url: https://www.linkedin.com/in/jit-kai-tan-6b2aba12a/
    affiliation: Singapore Management University Master of IT in Business
    affiliation_url: https://scis.smu.edu.sg/master-it-business
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                     eval = TRUE,
                     warning = FALSE,
                     message = FALSE,
                     fig.retina = 3)
```

```{r}
packages = c('ggstatsplot', 'tidyverse', 'ggside','ggdist','PMCMRplus','readxl','see','performance','parameters','report')
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
}
```

```{r}
exam_data <- read_csv("data/Exam_data.csv")
```

gghistostats
set.seed is used to ensure that when simulations are run when type = robust or bayes, the result is always the same

```{r}
set.seed(1234)

gghistostats(
  data = exam_data,
  x = ENGLISH,
  test.value = 60,
  xlab = 'English Scores'
)
```

two-sample mean tests:ggbetweenstats() , type = parametric or null
```{r}
ggbetweenstats(
  data = exam_data,
  x = GENDER,
  y = MATHS,

  messages = FALSE
)
```

One-way ANOVA Test (type => "np" or "non-parametric)

```{r}
ggbetweenstats(
  data = exam_data,
  x = RACE,
  y = ENGLISH,
  type = "np",
  mean.ci = TRUE,
  pairwise.comparisons = TRUE,
  pairwise.display = "all",
  p.adjust.methods = "fdr",
  messages = FALSE
)
```

```{r}
pairwise_comparisons(data = exam_data,
                     x = RACE,
                     y = ENGLISH,
                     type = "np")
```

Significant TEst of Correlation =>ggscatterstats()
```{r}
ggscatterstats(
  exam_data,
  MATHS,
  ENGLISH,
  marginal=TRUE
)
```


Significant Test of Association (Dependance) => ggbarstats()
```{r}

exam01 <- exam_data %>%
  mutate(MATHS_bins = 
           cut(MATHS,
               breaks = c(0, 60, 75, 85,100)))

ggbarstats(
  exam01,
  x = MATHS_bins,
  y = GENDER
)
```


Toyota Corolla

```{r}
car_resale <- read_xls("data/ToyotaCorolla.xls",
                       "data")
```

creating model

```{r}
model1 <- lm(Price ~ Age_08_04 + Mfg_Year + KM + Weight + Guarantee_Period, data = car_resale)
```

check for multi colinearity
```{r}
check_c <- check_collinearity(model1)
```

```{r}
plot(check_c)
```

Normality Check

```{r}
check_n <- check_normality(model1)
```

```{r}
check_h <- check_heteroscedasticity(model1)
```

check model

```{r}
check_model(model1)
```

plot

```{r}
plot(parameters(model1))

```


```{r}
ggcoefstats(model1,
            output = "plot")
```